---
title: "Deploying to connect via travis"
author: "Andrie de Vries"
date: "30/01/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objective

This document describes how to automatically deploy an artefact from Github to Connect, using Travis as the continuous integration tool.

## The sequence of events

Step:

1. Deploy your artefact to Connect using push-button deployment
2. Make a note of your API key and GUID from Connect, and configure these on Travis
3. Deploy programmatically on Travis

```{r, echo=FALSE}
library(DiagrammeR)

DiagrammeR("
sequenceDiagram;
  participant P as Project
  participant G as Github
  participant T as Travis
  participant C as Connect
  opt first deployment
    P->>C: push button deploy
  end
  opt copy env vars
    C-->>T: C_API_KEY
    C-->>T: C_SERVER
    C-->>T: GUID
  end
  opt programmatic deployment
    P->>G: commit and push;
    G-->>T: commit hook;
    T->>C: deploy using bash and API
  end
   
")
```

## Travis configuration

Steps:

1. Enable Travis deployment for your repo
2. Add your secret information as environment variables to Travis
3. Edit your `.travis.yml` file


### Relevant files {.tabset}

#### .travis.yml

The `.travis.yml` file basically just triggers the `deploy_to_connect.sh` script to deploy an artefact.


```{r engine='bash', echo=FALSE, comment="", include=FALSE}
cat .travis.yml
```

#### deploy_to_connect.sh

And the `deploy_to_connect.sh` looks like this:


```{r engine='bash', echo=FALSE, comment="", include=FALSE}
cat deploy_to_connect.sh
```

## Conclusion

foo
